A flexible integer linear programming formulation for scheduling clinician on-call service in hospitals

### 2020-06-03 paper/paper.comparison.tex
Outline Bilgin2008 paper in comparisons

Using the classification in [ref-De Causmaecker and Berghe], we compare our clinician
scheduling problem and solution approach with existing literature. Azaiez and Al Sharif [ref]
describe a nurse rostering problem to schedule nurses on a per-day basis, for a total period
of 28 days. In this problem, they are required to assign a minimum number of staff members
per day, unlike in our clinician scheduling problem. Similar to our problem, they include
hard constraints to prevent consecutive assignments, and enforce a minimum and maximum 
number of shifts for each nurse. When formulating the optimization goal, Azaiez and Al Sharif
focus on balancing the workload among nurses, preventing day-night consecutive shifts and avoiding
off-on-off assignments. Their formulation does not incorporate nurse preferences
for time off into the model.

[...]

>>>>

Using the classification in [ref-De Causmaecker and Berghe], we compare our clinician
scheduling problem and solution approach with existing literature. Azaiez and Al Sharif [ref]
describe a nurse rostering problem to schedule nurses on a per-day basis, for a total period
of 28 days. De Causmaecker and Berghe classify this problem as $ASBN/V2/PL$.
In this problem, they are required to assign a minimum number of staff members
per day, unlike in our clinician scheduling problem. Similar to our problem, they include
hard constraints to prevent consecutive assignments, and enforce a minimum and maximum 
number of shifts for each nurse. When formulating the optimization goal, Azaiez and Al Sharif
focus on balancing the workload among nurses, preventing day-night consecutive shifts and avoiding
off-on-off assignments. Their formulation does not incorporate nurse preferences
for time off into the model.

In [ref-Bilgin 2008], Bilgin et al address a nurse rostering problem using local search. 
The problem presented is classified as $ASBI/RVNO/PLR$.
Some of the constraints they incorporate include coverage constraints, overlapping assignment
constraints and horizontal constraints, which include constraints arising from employment contracts
(such as satisfying minimum and maximum thresholds and limiting consecutive assignments). Unlike
our problem, Bilgin et al consider coverage constraints to be soft constraints, in order to prevent
over-constraining of the problem. They incorporate nurse requests into the model formulation,
similar to our problem, but they allow requests for both time off and time on.
[...]
